Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-27 draft/ms_alexie.tex
More edits from Alexie

    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope. 
    The Wide layer of the SSP is both wide and deep, reaching a detection limit of 
    $i>26.0$ mag. 
    At these depths, it is challenging to achieve accurate, unbiased, and consistent
    photometry across all five bands. 
    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
    being designed by the Large Synoptic Survey Telescope’s Data Management system. 
    We have developed a \texttt{Python}-based, flexible framework to inject synthetic
    galaxies into real HSC images called \synpipe{}. 
    In this paper, we explain the design and implementation of \synpipe{} and generate 
    a sample of synthetic galaxies to examine the photometric performance of the HSC
    pipeline. 
    For stars, we achieve 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at
    $i{\sim}25.5$ in the $i$-band (corresponding to uncertainties of ${\sim}0.01$ and 
    ${\sim}0.06$ mag respectively).  
    For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
    achieves 7\% photometry at $i{\sim}20.0$ mag and 11\% photometry at $i{\sim}25.0$ 
    in the $i$-band (corresponding to uncertainties of ${\sim}0.14$ and ${\sim}0.20$ 
    mag respectively). 
    We show that both \forced{} PSF and \cmodel{} photometry yield unbiased color 
    estimates that are robust to seeing conditions. 
    We identify several caveats that apply to version \texttt{4.0.2} of the HSC 
    pipeline and they need to be considered when using data from the first public 
    HSC data release. 
    First, the degree to which an object is blended with other objects impacts the 
    overall photometric performance.  
    This is especially true for point sources. 
    Highly blended objects tend to have larger photometric uncertainties, 
    systematically underestimated fluxes and slightly biased colors. 
    Second, $>20$\% of stars at $22.5< i < 25.0$ mag can be misclassified as 
    extended objects.
    Third, the current \cmodel{} algorithm tends to strongly underestimate the 
    half-light radius and ellipticity of galaxies with $i>21.5$ mag.

@@

\alexie{ALEXIE EDITED TO HERE}

@@

    In Fig \ref{fig:psf_color}, we evaluate the accuracies of the \forced{} $(g-i)$
    and $(i-y)$ PSF colors via comparing the error in color measurements with both
    input magnitudes and input colors.
    These results suggest that \hscpipe{} provides accurate and unbiased PSF color
    estimates for synthetic stars with realistic color distributions down to very 
    faint magnitude.
    For $(g-i)$ color, the average uncertainty around $i_{\mathrm{Input}}{\sim}19.0$ 
    mag is ${\sim}0.025$ mag, and it increases to ${\sim}0.11$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag.
    The $(i-y)$ color shows very similar results.
    We also find that the accuracies of PSF colors do not depend on the input colors 
    of the synthetic stars or the seeing conditions.
    For instance, the accuracy of $(g-i)$ color for the bad-seeing \tract{} is only
    slightly worse in the very faint end (${\sim}0.14$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the results for the 
    good-seeing \tract{}.

    We further illustrate the accuracies of PSF colors via comparing the distributions
    of colors for the input synthetic stars and the stars recovered by \hscpipe{}
    (see Fig \ref{fig:psf_cdist}).
    Using four different colors and two color--color planes, we show that the 
    \forced{} PSF colors can accurately reproduce the distributions of all four colors 
    and the color-color distributions.

    As for the highly blended stars, on Fig \ref{fig:psf_color}, we see that on average
    they still have larger uncertainties in colors compared to the relatively isolated
    ones.
    For $(g-i)$ color, the average color uncertainty is ${\sim}0.1$ mag larger for the
    highly blended stars at a fixed input magnitude.
    Also, for blended stars, the $(g-i)$ color biases toward bluer end while the 
    $(i-y)$ color biases toward redder end.
    However, the biases in color measurements for highly blended stars are less severe 
    than their magnitude measurements.
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic galaxies and the $log(S/N)$ measured by \hscpipe{}
        \cmodel{} photometry.
        The lines and contours legend is similar to Fig \ref{fig:star_sn}
        }
    \label{fig:cmodel_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Color-Color Distributions of the Input and Measurements for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_cdist}
    \end{center}
    \caption{
        Evaluations of color measurement accuracy for synthetic galaxies
        using the color-color distributions.
        The \textbf{left} panel (a) uses $(g-r)$ vs. $(r-i)$ colors, and the 
        \textbf{right} panel (b) uses $(i-z)$ and $(z-y)$ colors.
        The filled contours and shaded histograms reflect the distributions for input
        colors.
        The empty contours and solid-line histograms show the distributions recovered
        by \hscpipe{} \cmodel{} photometry.
        }
    \label{fig:cmodel_cdist}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    For galaxies, \hscpipe{} uses a \cmodel{} photometry algorithm that is an improved 
    version of the SDSS \cmodel{} photometry.
    For more details, please see Bosch\etal (in prep.).
    In short, \cmodel{} tries to fit each object using the combination of a
    de~Vaucouleurs and an exponential profiles that are approximated by multiple 
    Gaussian profiles.
    Despite the limitation of the \cmodel{} method (e.g., sensitive to background
    subtraction and deblender failure), it can deliver robust PSF-corrected fluxes and
    colors for galaxies.

    In our tests, we randomly inject ${\sim}40,000$ synthetic galaxies into each
    \tract{}; and, using an approach similar to that for synthetic stars, we select 
    galaxy samples for photometric comparisons.
    First, ${\sim}3$--$7$\% of the synthetic galaxies are located within 2 pixels 
    of the centroids of real objects or do not show any match in the \synpipe{} 
    results, they are hence removed from the sample.
    The fraction of unmatched objects slightly increases with worse seeing condition.

    After selecting the matched synthetic galaxies with primary detection and
    clean photometry (see Appendix \ref{app:qc} for details), we have ${\sim}30,000$
    galaxies in each \tract{} for comparison.
    \hscpipe{} misclassifies less than $1$\% of these objects as point sources
    in the good-seeing \tract{}.
    But the fraction of misclassified galaxies increases to $4$\% in the
    bad-seeing \tract{}.
    The median input magnitude for these misclassified sources is ${\sim}24.9$ mag
    in $i$-band, significantly fainter than the median of other sources.
    We further discuss this in Section \ref{ssec:sg}.

    We also use $b>0.05$ to define samples of highly blended galaxies.
    Due to the extended nature of the galaxies, the $b$ distributions for synthetic 
    galaxies skew toward higher values (especially for the bad-seeing \tract{}) than
    the ones for stars.
    About $7$--$9$\% of synthetic galaxies are highly blended by this standard.
    The fraction is only slightly higher in the bad-seeing \tract{}, and the
    $g$-band has the highest fraction of highly blended galaxies.
    We highlight the highly blended ones in comparisons, and there are other relevant
    discussions in Section \ref{ssec:blendedness}.

    Although these galaxies span in very wide large ranges of magnitude and
    structural parameters, the majority of them are faint
    ($i_{\mathrm{Input}} > 24.0$ mag) and small ($R_{\mathrm{e}} < 0.5$\asec).
    It is very challenging to obtain good photometric quality of these galaxies, which 
    is crucial to key scientific goals of the HSC survey.
    The selected samples do not provide enough bright or large galaxies to test.
    Therefore, we will supplement results for these galaxies using better samples
    in the future.

@@

    In Fig \ref{fig:cmodel_sn}, we first show the relation between the input
    magnitudes and the \s2n{} of the synthetic galaxies estimated by the ratio
    between \cmodel{} flux and its uncertainty.
    The \s2n{} used here is the average one for extended object.

    We still use $i$ and $g$ bands as examples.
    As PSF magnitude for stars, \cmodel{} photometry establishes well-behaved relation 
    between input magnitude and output \s2n{}. 
    Comparing to stars, the \s2n{} from \cmodel{} for synthetic galaxies shows larger
    scatter at fixed input magnitude, which is likely due to differences in size and 
    shape of the galaxies.
    This makes it difficult to define ``detection limit'' for galaxies clearly.

    In $i$ band, typical $25.2$ mag galaxy has \s2n{}${\sim}20$ from \cmodel{}, but 
    there are already galaxies at the same magnitude have \s2n{} below 5.
    Although HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag, the 
    sample will be incomplete at this faint magnitude.
    It also introduces selection bias if galaxies with certain structural properties 
    are harder to detect than others.
    HSC survey data users who want to select flux-limited galaxy sample,
    or intend to study the population of faint (e.g., high-$z$) galaxies should
    keep this in mind.
    Similar to stars, worse seeing also leads to lower \s2n{} at fixed magnitude 
    (see Fig \ref{fig:psf_s2n} for $i$-band).

@@

    In Fig \ref{fig:cmodel_mag}, we illustrate the photometric uncertainties of the
    \cmodel{} magnitudes in each band using the same format for Fig \ref{fig:psf_mag}.

    The overall performance of \cmodel{} photometry is reasonable down to 
    $i_{\mathrm{Input}}=25.2$ mag.
    Compared to PSF photometry for stars, the uncertainties of \cmodel{} show larger 
    scatter for galaxies, which is expected given the diversity of structural 
    properties and complexities in the model-fitting process.
    At the same time, \cmodel{} algorithm in \hscpipe{} provides unbiased and consistent 
    photometry for galaxies in different bands and seeing conditions.

    In $i$-band, the typical flux accuracy for \forced{} \cmodel{} is ${\sim}7-9$\%
    in the good-seeing \tract{} at $i_{\mathrm{Input}}<24.0$ mag, and moderately 
    decreases to ${\sim}11$\% at $25.0$ mag.
    and ${\sim}9$\% at $i_{\mathrm{Input}}{\sim}24.0$ mag.
    For the bad-seeing \tract{} in $i$-band, the performance is very similar.
    At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the median magnitude offset
    between output and input values changes from \plus{}$0.041$ mag to
    \minus{}$0.005$ mag, which suggests that \forced{} \cmodel{} photometry is
    unbiased down to the very faint end.

    It is worth noting that the flux uncertainty from \synpipe{} is significantly 
    larger than the flux error from \hscpipe{}, which does not take into account the 
    systematic uncertainties involved in the modeling fitting process.
    Although the synthetic galaxies here are described by simple single-\ser{} model, 
    \cmodel{} algorithm can only approximate them to certain accuracy, especially when 
    background noise, deblending uncertainty, and priors of model parameters are 
    considered.
    Given that real galaxies are more complex in structure, these uncertainties should 
    be treated as lower limits.

@@

    The accuracy of \forced{} \cmodel{} photometry is consistent across all filters.
    For $g$, $r$, and $z$ bands, the photometric uncertainties are very similar to
    $i$-band results between $20.0$ and $25.0$ mag.
    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
    across the entire input magnitude range.
    The uncertainties for $y$ band are slightly worse, ranging from 9\% to 17\% in the
    same magnitude bins.
    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
    $y$ band at $>24.0$ mag.
    Average magnitude offsets change from \minus{}0.06 at $24.0$ mag to \minus{}0.22
    mag at 25.0 mag.
    Both a worse seeing condition and a higher background noise level can make it more
    difficult to detect faint object in $y$ band.
    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
    around the detection threshold.

    As mentioned, the statistics for brighter galaxies are uncertain due to small 
    sample size.
    We do notice that, at $i_{\mathrm{Input}}<20.0$, the \forced{} \cmodel{} photometry 
    shows larger uncertainty and starts to systematically underestimate the total flux.
    Based on external comparisons, the behavior of \cmodel{} for bright galaxies may 
    depend on the galaxy type (e.g., \citealt{HSCDR1}). 
    Known issues of current \hscpipe{} (e.g., \hscpipe{} over-deblends around bright 
    objects; inappropriately weights priors in \cmodel{}) could lead to poorer 
    photometric quality for bright galaxies. 
    Meanwhile, at the imaging depth of HSC ($>29.0$\sb{} in $i$ band for Wide layer), 
    assumptions in \cmodel{} may no longer be the best choice for modeling bright 
    galaxies (e.g., for massive elliptical galaxies; see Huang\etal in prep.~for 
    more details).
    We will look into these issues more carefully in the future.

    For the highly blended galaxies, we also see systematically underestimated total 
    flux (average offset ${\sim}0.1$ mag) and larger scatter of photometric 
    uncertainty in all five bands.
    Meanwhile, the contrast between relatively isolated and highly blended galaxies
    in photometric performance is not as staggering as the one for synthetic
    stars (Fig \ref{fig:psf_mag}).

    We also test the \unforced{} \cmodel{} photometry in all five bands, and the
    results suggest similar accuracies.
    We highlight the differences between \forced{} and \unforced{} \cmodel{}
    photometry in $g$ and $y$ bands in Fig \ref{fig:cmodel_diff}.
    The only noticeable feature is for galaxies brighter than $24.0$ mag in
    $g$ band, the \forced{} \cmodel{} magnitudes are systematically brighter than
    the \unforced{} ones, suggesting \forced{} \cmodel{} shows better accuracy in 
    $g$ band.

@@

    The consistent and accurate five-band \cmodel{} colors from \hscpipe{} are crucial
    to the photometric redshift and spectral energy distribution (SED) fitting results.
    They are also key to the selection of high-$z$ Lyman-break galaxies (LBG) and
    and many other interesting objects.

    In Fig \ref{fig:cmodel_color}, we demonstrate the accuracies of \forced{} $(g-i)$
    and $(i-y)$ \cmodel{} colors in the same format for synthetic stars
    (Fig \ref{fig:psf_color}).
    They confirm that \hscpipe{} can provide reliable \cmodel{} colors for synthetic 
    galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
    For $(g-i)$ colors, the average uncertainty at $i_{\mathrm{Input}}{\sim}21.0$ mag
    is ${\sim}0.04$ mag.
    The uncertainty increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}25.0$ mag.
    $(i-y)$ colors show similar results.

    The performance of \forced{} \cmodel{} color does not depend on seeing and is 
    unbiased for entire ranges of input magnitudes and colors.
    The only noticeable feature is that the $(i-y)$ color at $i_{\mathrm{Input}}>24.0$ 
    is slightly overestimated.
    As mentioned above, this is not surprising given the shallower imaging depth in
    $y$ band.
    Meanwhile, high blendedness also increases the color uncertainties and biases the 
    color measurements.
    The highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder  
    $(i-y)$ colors than the input ones.

    Similar to Fig \ref{fig:psf_cdist}, we also compare the color--color distributions
    of the input and output \forced{} \cmodel{} values in Fig \ref{fig:cmodel_cdist}.
    The general 2--D distributions are well recovered but the accuracy is not as good as 
    the one for stars, especially on the $(i-z)$ vs. $(z-y)$ plane.
    This is expected given the narrow dynamical ranges of these colors among red filters.
    The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
    colors at the very ``blue'' end, while overestimating the $(i-y)$ color at the very
    red end.

    We should point out that we assume constant color for the entire galaxy.
    In reality, different colors for individual component or color gradient can 
    complicate the situation.
    The uncertainties of \cmodel{} colors here should be considered as lower limits.
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Astrometric Calibration
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_astrometry}
    \end{center}
    \caption{
        Astrometric accuracy for a synthetic star (\textbf{left}) and a galaxy
        (\textbf{right}) via the differences in R.A and Dec between the input
        coordinates and the ones measured on the \coadd{} images.
        Hexagonal bins (filled histogram) and contours (solid-line histogram) are for
        the synthetic objects from \tracts{} with good and bad seeing conditions, 
        respectively.
        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.
        }
    \label{fig:astrometry}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star-Galaxy Separation
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_galaxy}
    \end{center}
    \caption{
        Problems with the current  \hscpipe{}star--galaxy separation method, which is 
        based on the magnitude difference between the PSF and \cmodel{} photometry.
        The plot on the \textbf{left} (a) illustrates distributions for the synthetic 
        stars.
        Hexagonal bins and filled histogram show distributions of correctly classified
        synthetic stars in the good-seeing \tract{}.
        The scatter plot (dashed-line histogram) and contour (solid-line histogram)
        show distributions of synthetic stars that are misclassified as extended
        objects in \tracts{} with bad and good seeing conditions, respectively.
        The plot on the \textbf{right} (b) illustrates distributions for synthetic 
        galaxies.
        Hexagonal bins (filled histogram) and contours (solid-line histogram)
        are for galaxies from good- and bad-seeing \tracts{}, respectively.
        The scatter plot and dashed-line histogram are for synthetic galaxies that are
        misclassified as point sources.
        Zero magnitude difference is highlighted using dashed lines on both plots.
        }
    \label{fig:sg}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Relations between Blendedness and Photomertic Errors
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_blendedness_err}
    \end{center}
    \caption{
        The relation between the $\log(\mathrm{Blendedness})$ parameter
        and the photometric accuracies for synthetic stars (\textbf{upper row}, a and 
        b) and galaxies (\textbf{lower row}, c and d) .
        The \textbf{left} column (a and c) is for uncertainties of PSF or \cmodel{} 
        magnitude, and the \textbf{right} column (b and d) is for uncertainties of 
        $(g-i)$ color.
        Hexagonal bins and contours show results for good- and bad-seeing
        \tracts{}, respectively.
        $\log(\mathrm{Blendedness}) = -1.0$ is marked using a vertical dashed line.
        }
    \label{fig:blend}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope. 
    The Wide layer of the SSP is both wide and deep, reaching a detection limit of 
    $i>26.0$ mag. 
    At these depths, it is challenging to achieve accurate, unbiased, and consistent
    photometry across all five bands. 
    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
    being designed by the Large Synoptic Survey Telescope’s Data Management system. 
    We have developed a \texttt{Python}-based, flexible framework to inject synthetic
    galaxies into real HSC images called \synpipe{}. 
    In this paper, we explain the design and implementation of \synpipe{} and generate 
    a sample of synthetic galaxies to examine the photometric performance of the HSC
    pipeline. 
    For stars, we achieve 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at
    $i{\sim}25.5$ in the $i$-band (corresponding to uncertainties of ${\sim}0.01$ and 
    ${\sim}0.06$ mag respectively).  
    For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
    achieves 7\% photometry at $i{\sim}20.0$ mag and 11\% photometry at $i{\sim}25.0$ 
    in the $i$-band (corresponding to uncertainties of ${\sim}0.14$ and ${\sim}0.20$ 
    mag respectively). 
    We show that both \forced{} PSF and \cmodel{} photometry yield unbiased color 
    estimates that are robust to seeing conditions. 
    We identify several caveats that apply to version \texttt{4.0.2} of the HSC 
    pipeline that need to be taking into consideration when using data from the first public 
    HSC data release. 
    First, the degree to which an object is blended with other objects impacts the 
    overall photometric performance.  
    This is especially true for point sources. 
    Highly blended objects tend to have larger photometric uncertainties, 
    systematically underestimated fluxes and slightly biased colors. 
    Second, $>20$\% of stars at $22.5< i < 25.0$ mag can be misclassified as 
    extended objects.
    Third, the current \cmodel{} algorithm tends to strongly underestimate the 
    half-light radius and ellipticities of galaxies with $i>21.5$ mag.

@@

@@

    In Fig \ref{fig:psf_color}, we evaluate the accuracy of the \forced{} $(g-i)$
    and $(i-y)$ PSF colors by comparing the error in color measurements with the input magnitudes colors. Figure  \ref{fig:psf_color} shows that \hscpipe{} provides accurate and unbiased PSF color
    estimates for synthetic stars with realistic color distributions down to very 
    faint magnitudes. The average uncertainty for $(g-i)$ is  ${\sim}0.025$ mag for $i_{\mathrm{Input}}{\sim}19.0$. This uncertainty increases to ${\sim}0.11$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag.  The $(i-y)$ color displays similar uncertainties. Figure \ref{fig:psf_color} also shows that the accuracy of the PSF colors do not depend on the input colors of the synthetic stars or the seeing conditions. For instance, the accuracy of $(g-i)$ for the bad-seeing \tract{} is only
    slightly worse in the very faint end (${\sim}0.14$ mag at
    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the 
    good-seeing \tract{}.

Figure \ref{fig:psf_cdist} displays the uncertainties in PSF colors  by comparing the color distributions of the input synthetic star sample to the recovered color distributions. Using four different colors and two color--color planes, we show that the 
    \forced{} PSF colors accurately recover the distributions of all four colors 
    and the color-color distributions.

    As for highly blended stars, Fig \ref{fig:psf_color} also shows that highly blended stars have larger uncertainties in their colors compared to isolated stars. At fixed input magnitude, the  uncertainty in $(g-i)$ is ${\sim}0.1$ mag larger for highly blened stars, Also, for blended stars, $(g-i)$ shows a bias towards bluer colors, while $(i-y)$ shows a bias towards redder colors. However, such biases appear to be less severe in terms of colors than in terms of magnitudes.

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic galaxies $log(S/N)$ as measured by \hscpipe{} \cmodel{} photometry. Lines and contours are similar to Fig \ref{fig:star_sn}
        }
    \label{fig:cmodel_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Color-Color Distributions of the Input and Measurements for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_cdist}
    \end{center}
    \caption{Color-color distributions of synthetic  galaxies.
        The \textbf{left} panel (a) uses $(g-r)$ vs. $(r-i)$ colors, and the 
        \textbf{right} panel (b) uses $(i-z)$ and $(z-y)$ colors. Filled contours and shaded histograms  correspond to the input colors. Empty contours and solid-line histograms show the distributions recovered
        by \hscpipe{} \cmodel{} photometry.
        }
    \label{fig:cmodel_cdist}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    For galaxies, \hscpipe{} uses a \cmodel{} photometry algorithm that is an improved 
    version of the SDSS \cmodel{} photometry.
    For more details, please see Bosch\etal (in prep.).
    In short, \cmodel{} tries fits object using both a de~Vaucouleurs and an exponential profile.  The \cmodel{} algorithm then fits a linear combination of these two best fit models. Despite the limitations of the \cmodel{} method (e.g., sensitivity to the background
    subtraction and to deblending failures), it can deliver robust PSF-corrected fluxes and
    colors for galaxies.

    We randomly inject ${\sim}40,000$ synthetic galaxies into each
    \tract{}; and, using an approach similar to that for synthetic stars, we select 
    galaxy samples for photometric comparisons. Synthetic galaxies that are located within 2 pixels 
    of the centroids of real objects are removed from the sample  (these represent ${\sim}3$--$7$\% of the input sample). After imposing quality cuts on the  recovered synthetic galaxy sample (see Appendix \ref{app:qc} for details), we have ${\sim}30,000$
    galaxies in each \tract{}.

    We find that \hscpipe{} mis-classifies less than $1$\% of these objects as point sources
    in the good-seeing \tract{}.
    But the fraction of misclassified galaxies increases to $4$\% in the
    bad-seeing \tract{}. We will discuss star/galaxy separation further in Section \ref{ssec:sg}.

    We define a sample of highly blended galaxies  by imposing the cut $b>0.05$.
    Due to the extended nature of galaxies, the $b$ distribution of synthetic 
    galaxies is more skewed toward high values (especially for the bad-seeing \tract{}) compared to the b distribution of stars.
    About $7$--$9$\% of synthetic galaxies are highly blended with $b>0.05$.
    The fraction is only slightly higher in the bad-seeing \tract{}, and the
    $g$-band has the highest fraction of highly blended galaxies \alexie{I don't understand here. Is this just a question of seeing? Is thid because the g-band has worse seeing. It seems in contradiction with the previous phrase.}. In our plots, we will highlight highly blended galaxies and we will discuss blending effects further in Section \ref{ssec:blendedness}.

% ALEXIE: not necessary
    %The majority of the galaxies in our synthetic galaxy samples are  are faint
    %($i_{\mathrm{Input}} > 24.0$ mag) and small ($R_{\mathrm{e}} < 0.5$\asec).
    %It is very challenging to obtain accurate photometry good photometric quality of these galaxies, which 
    %is crucial to key scientific goals of the HSC survey.
    %The selected samples do not provide enough bright or large galaxies to test.
    %Therefore, we will supplement results for these galaxies using better samples
    %in the future.

@@

    Figure \ref{fig:cmodel_sn} shows the relation between the input
    magnitudes and the \s2n{} of synthetic galaxies.  The  \s2n{} is the ratio  of the \cmodel{} flux and its uncertainty.    The \s2n{} used here is the average one for extended object. \alexie{What do you mean here? You have a clound of points for each object, not a mean value of SN per mag bin. Needs to be calrified.}

 Figure  \ref{fig:cmodel_sn} shows  that the \cmodel{} photometry displays a well-behaved relation between input magnitude and output \s2n{}.  Compared to stars, the \s2n{} from \cmodel{} for synthetic galaxies shows a larger
    scatter at fixed input magnitude. This is likely due to the fact that galaxies have a wider range in sizes and shapes than point sources.  In $i$ band, a typical $25.2$ mag galaxy has \s2n{}${\sim}20$ from \cmodel{}, but 
    there are also galaxies at the same magnitude which have \s2n{} below 5. The HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag but the 
    sample becomes incomplete at these faint magnitudes.
    It also introduces a selection bias if galaxies with certain structural properties  (e.g., more extended and lower surface brightness)
    are harder to detect than others.
    HSC survey data users who want to select flux-limited galaxy samples,
    or who intend to study the population of faint (e.g., high-$z$) galaxies should
    keep this in mind.  Finally, we also find that  a worse seeing leads to a lower \s2n{} at fixed magnitude 
    (see Fig \ref{fig:psf_s2n} for $i$-band).

@@

    Fig \ref{fig:cmodel_mag} shows the photometric uncertainties of the
    \cmodel{} magnitudes in each band using the same format as Fig \ref{fig:psf_mag}.

    The overall performance of \cmodel{} photometry is reasonable down to 
    $i_{\mathrm{Input}}=25.2$ mag.
    Compared to the PSF photometry for stars, the uncertainties of \cmodel{} show larger 
    scatter for galaxies, which is expected given the diversity of galaxy shapes and sizes which adds complexity to the model-fitting process.
    At the same time, Figure \ref{fig:cmodel_mag} shows that the \cmodel{} algorithm in \hscpipe{} provides unbiased and consistent 
    photometry for galaxies across different bands and seeing conditions.

The typical $i$-band flux accuracy for \forced{} \cmodel{} is ${\sim}7-9$\% in the good-seeing \tract{} at $i_{\mathrm{Input}}<24.0$ mag. This moderately degrades to ${\sim}11$\% at $25.0$ mag. The performance is similar in the $i$-band bad-seeing \tract{}. At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the median magnitude offset
    between output and input values changes from \plus{}$0.041$ mag to
    \minus{}$0.005$ mag, which suggests that \forced{} \cmodel{} photometry is
    unbiased down to the very faint end.

    It is worth noting that the flux uncertainty from \synpipe{} are significantly 
    larger than the flux errors from \hscpipe{}, which does not take into account the 
    systematic uncertainties involved in the modeling fitting process. Even though our synthetic galaxy sample is  comprised of objects with simple single-\ser{} models, 
    \cmodel{} algorithm can only approximate them to a certain accuracy because of the background noise, deblending uncertainties, and priors imposed on model parameters. Given that real galaxies are more complex in structure, the uncertainties derived from our \synpipe{} tests should be treated as lower limits.

\alexie{What does this say about the values of SN from CMODEL then? If the unceratinties are underestimated, then the SN is overestimated? By how much? WOrth commenting on here?}

@@

    The accuracy of \forced{} \cmodel{} photometry is consistent across all filters.
    For the$g$, $r$, and $z$ bands, the photometric uncertainties are very similar to
    $i$-band results between $20.0$ and $25.0$ mag.
    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
    across the entire input magnitude range.
    The uncertainties for the $y$ band are slightly worse, ranging from 9\% to 17\% in the
    same magnitude bins.
    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
    the $y$ band at $>24.0$ mag. This bias in the $y$ band flux is equal to  \minus{}0.06 at $24.0$ mag to \minus{}0.22
    mag at 25.0 mag. Worse seeing conditions and a  higher background noise level mean that it is more
    difficult to detect faint objects in the $y$ band.
    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
    around the detection threshold.

Our synthetic galaxy sample is dominated by faint galaxies.  Hence, we have poor statistics for bright galaxies. However, we do find that at $i_{\mathrm{Input}}<20.0$, the \forced{} \cmodel{} photometry starts to systematically underestimate total fluxes. Based on external comparisons, the behavior of \cmodel{} for bright galaxies may 
    depend on galaxy types (e.g., \citealt{HSCDR1}).  Also, at bright magnitudes, another known issue is that the current \hscpipe{} (e.g., \hscpipe{} over-deblends around bright 
    objects. Inappropriately weight priors in \cmodel{}) may also lead to poorer photometric quality for bright galaxies.  Finally, at the imaging depth of HSC ($>29.0$\sb{} in the Wide Layer $i$ band),  \cmodel{} may simply not be a good choice for modeling bright 
    galaxies (e.g., for massive elliptical galaxies; see Huang\etal in prep.~for 
    more details).

We also find that highly blended galaxies tend to have systematically underestimated total 
    fluxes (with an average offset ${\sim}0.1$ mag) and larger photometric uncertainties in all five bands. However,  the contrast between relatively isolated and highly blended galaxies
    in photometric performance is not as stark as for synthetic
    stars (Fig \ref{fig:psf_mag}).

    We also test the \unforced{} \cmodel{} photometry in all five bands, and the
    results suggest similar accuracies.

    Fig \ref{fig:cmodel_diff} compared the difference between  \forced{} and \unforced{} \cmodel{} in $g$ and $y$.  We find that  \forced{} and \unforced{} \cmodel{} shows similar trends.  The main  noticeable trend is that galaxies brighter than $24.0$ mag in $g$ band, have systematically brighter \forced{} \cmodel{} magnitudes. This suggests that the \forced{} \cmodel{} is more accurate in the $g$ band.

@@

    Consistent and accurate five-band \cmodel{} colors from \hscpipe{} are crucial  for photometric redshift and spectral energy distribution (SED) estimates. They are also key, for example, to the selection of high-$z$ Lyman-break galaxies (LBG) .

    Fig \ref{fig:cmodel_color} evaluates the  accuracy of \forced{} $(g-i)$ and $(i-y)$ \cmodel{} colors using the same format as Figure Fig \ref{fig:psf_color}. We find that \hscpipe{} provides reliable \cmodel{} colors for synthetic 
    galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
    For $(g-i)$ colors, the average uncertainty at $i_{\mathrm{Input}}{\sim}21.0$ mag
    is ${\sim}0.04$ mag.
    The uncertainty increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}25.0$ mag.
    The $(i-y)$ colors show similar results.

    The performance of \forced{} \cmodel{} color does not depend on seeing and is 
    unbiased for the entire range of magnitudes and colors that we have tested.
    The only noticeable feature is that the $(i-y)$ color at $i_{\mathrm{Input}}>24.0$ 
    is slightly overestimated.
    As mentioned above, this is not surprising given the shallower $y$ band imaging depth. Highly blended galaxies have larger uncertainties in their colors compared to isolated galaxies.  Highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder  
    $(i-y)$ colors compared to their input colors.

Figure  \ref{fig:cmodel_cdist} compare the input color--color distributions with the recovered color distributions. The general 2--D distributions are well recovered but the accuracy is not as good as for stars, especially in the $(i-z)$ vs. $(z-y)$ plane.
    This is expected given the narrow dynamical ranges of these colors in the redder filters.
    The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
    colors at the very ``blue'' end, while overestimating the $(i-y)$ color at the very
    red end.

We note that  our synthetic galaxies do not have color gradients.  In reality, color gradients will complicate the situation and hence the uncertainties shown here should be considered as lower limits.
